### 2021-07-15 src/paper/results/validation.tex

>>>>

Another form of validating our model is to see how well our main results align with
other studies that evaluate the effect of large scale rapid testing. Of course, this
has to be taken with a grain of salt as the effect of any rapid testing policy depends
on the incidence of the disease in the population, how well other testing policies
such as PCR tests are working, the effect of seasonality and NPIs that are in place.

Nevertheless, it is reassuring that other studies find effect sizes in the same order
of magnitude.

\citet{Pavelka2021} estimates that a mass testing campaign in Slovakia in October and
November 2020 where approximately 65 \% of the population took a rapid test within a two
week period lead to a reduction in case numbers of 70 \% three weeks after the start
of the intervention. Moreover, they find that this strong reduction in
cases cannot be explained by isolation of people who tested positive alone but only when
they took into account that household members of people who tested positive reduced
their contacts.

While we do not model the exact scenario of \citet{Pavelka2021}, we can roughly compare
their estimates with our predictions for the difference between the baseline scenario
and and a scenario without rapid tests. In May about 45\% of people do
at least one rapid test in every week. Taking into account that there are many repeated
testers the number of people who do a test within a two week period is probably
slightly less than the 65 \% from the intervention in Slovakia. On the other hand, we
have many people who do more than one rapid test in that time which also leads to the
detection of cases. Our model predicts that the observed incidence with tests is
approximately 65 \% lower than without tests after three weeks.
Thus we have an effect size in the same order of magnitude but are slightly
less optimistic regarding the efficiency of rapid test.

\citet{Berger2021} analyse the effect of twice weekly rapid testing in schools. They
have two main findings: Firstly, rapid tests reduced the share of undetected cases
among students by a factor between 2 and 4. Secondly, open schools with mandatory
testing might leads to the same or even lower numbers of infections than closed
schools. The estimates are based on infection numbers after the Easter holiday.

Again, we do not directly simulated their scenarios but can roughly compare our results
to theirs. We estimate a share of undetected cases of approximately 75 \% among school
age children (5 to 14 years) at the beginning of April, see
Figure~\ref{fig:share_known_cases_by_age_group}. This drops to slightly less than 40 \%
at the end of our simulation period. Thus in the long run, mandatory tests at schools
led to a reduction of the share of undetected cases by a factor of more than 1.8 which
is just slightly below the factor of 2 to 4 predicted by \citet{Berger2021}.

Similarly we are slightly less optimistic for the effect opening schools with testing
compared to closing schools. While they predict that opening schools could even be
beneficial we estimate that it would lead to a slight increase in case numbers
see Figure~\ref{fig:school_scenarios_detailed}).

% In May 45 % per week are tested
% Incidence pessimistic = 1750
% Incidence with mass testing = 750
